---
title: "MyNorfolk Requests"
logo: assets/city-of-norfolk.png
format: dashboard

theme: 
  - cosmo
  - assets/styles/custom.scss
  - assets/styles/quarto.scss

execute: 
  echo: false
---

```{r setup, include = FALSE}
library(dplyr)
library(ggplot2)
library(forcats)

library(targets)
tar_source("R/formatting.R")
```

# Today

```{r load-targets-today}
#| include: false
tar_load(c(today_stats, today_plots))
```

## Row 

::: {.valuebox icon="arrow-repeat" color="vb-warning"}
In Progress

`r number(today_stats$n_in_progress_total)`

`r change(0, today_stats$n_in_progress_new, when = "were started today", more = NULL, less = NULL)`
:::


::: {.valuebox icon="plus-circle" color="vb-info"}
Opened

`r number(today_stats$n_opened)`

`r change(today_stats$n_opened_yesterday, today_stats$n_opened, when = "yesterday")`
:::

::: {.valuebox icon="check-circle" color="vb-success"}
Closed

`r number(today_stats$n_closed)`

`r change(today_stats$n_closed_yesterday, today_stats$n_closed, when = "yesterday")`
:::

::: {.valuebox icon="x-circle" color="vb-danger"}
Cancelled

`r number(today_stats$n_cancelled)`

`r change(today_stats$n_cancelled_yesterday, today_stats$n_cancelled, when = "yesterday")`
:::

## Row

### Column {.tabset width="50%"}

```{r today-top-new-requests}
#| title: Top New Requests
today_plots$top_new_requests
```

```{r today-top-in-progress}
#| title: Top In Progress
#| caption: These things are in progress right now.
today_plots$top_in_progress
```

```{r today-top-closed}
#| title: Top Closed Today
today_plots$top_closed
```

### Column

```{r today-opened-by-hour}
#| title: Opened by Hour of Day
today_plots$opened_by_hour
```

```{r today-resolved-by-hour}
#| title: Resolved by Hour of Day
today_plots$resolved_by_hour
```


# Week

```{r load-targets-week}
#| include: false
tar_load(c(week_stats, week_plots))
```

## Row 

::: {.valuebox icon="arrow-repeat" color="vb-warning"}
In Progress

`r number(today_stats$n_in_progress_total)`

`r change(0, week_stats$n_started, when = "were started this week", more = NULL, less = NULL)`
:::


::: {.valuebox icon="plus-circle" color="vb-info"}
Opened

`r number(week_stats$n_opened)`

`r change(week_stats$n_opened_prev, week_stats$n_opened, when = "last week")`
:::

::: {.valuebox icon="check-circle" color="vb-success"}
Closed

`r number(week_stats$n_closed)`

`r change(week_stats$n_closed_prev, week_stats$n_closed, when = "last week")`
:::

::: {.valuebox icon="x-circle" color="vb-danger"}
Cancelled

`r number(week_stats$n_cancelled)`

`r change(week_stats$n_cancelled_prev, week_stats$n_cancelled, when = "last week")`
:::

## Row

### Column {.tabset width="50%"}

```{r week-top-new-requests}
#| title: Top New Requests
week_plots$top_new_requests
```

```{r week-top-in-progress}
#| title: Top In Progress
#| caption: These things are in progress right now.
week_plots$top_in_progress
```

```{r week-top-closed}
#| title: Top Closed This Week
week_plots$top_closed
```

### Column

```{r week-opened-by-hour}
#| title: Opened by Hour of Day
week_plots$opened_by_hour
```

```{r week-resolved-by-hour}
#| title: Resolved by Hour of Day
week_plots$resolved_by_hour
```


# About

## Row

::: card
::: card-header
About MyNorfolk
:::
::: card-body
This dashboard is a demo of Quarto dashboards and **is not affiliated** with the city of Norfolk.

[MyNorfolk](https://www.mynorfolk.org/#/homepage) is a service that allows residents of [the City of Norfolk](https://www.norfolk.gov/) to request services online from their computer or mobile device.
The data used in this dashboard is available on the [Norfolk Open Data Portal](https://data.norfolk.gov/Government/MyNorfolk/nbyu-xjez).

> This dataset provides data from MyNorfolk, a citizen services portal that delegates and tracks requests and questions about the city of Norfolk and the services we provide to our residents, businesses, and visitors. Data for the service requests is collected from phone calls, emails, an app for smart phones and on-line. The portal is managed by the Norfolk Cares Center; its mission is to provide a single point of contact for visitors, residents, businesses and city staff to request a city service, report a concern, seek information about Norfolk, or follow-up on a previous request for service.
>
> **Disclaimer** - With the current process in place, not all tickets are closed automatically. There could be tickets shown as open in this dataset that are closed in our other systems. We are working to address the issue.
:::
:::

::: card
::: card-header
About this dashboard
:::
::: card-body
This dashboard is built with [Quarto Dashboards](https://quarto.org/docs/dashboards/),
a new output format to be released in [Quarto 1.4](https://quarto.org/docs/download/prerelease.html).
The dashboard is updated regularly and published on [Quarto Pubs](https://quartopub.com/).

[<i class="bi bi-github"></i> Source code](https://github.com/gadenbuie/mynorfolk-dash)
:::
:::
